Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-09 ii/paper/paper.tex
Stuff

\section{Probabilistic Search}

>>>>

\subsection{Probabilistic Search}

While using VOSH for probabilistic search a new problems become apparent that have not been addressed yet.
VOSH is not and cannot be capable of deciding, which of two siblings at each level is more optimal.
To solve this problem, the authors of~\cite{inproc:main} introduce an additional data structure $M$, which is a max-heap operating on a key-value pairs.
The key is the probability of flips in page $u$ for set $S$, while the value is the actual value $S$.
M is populated with tuples generated by the $h$ root nodes of VOSH trees.

Using this methodology they test their implementation on an 8B web page corpus, with 64 bit hashes and various Hamming distances.
They then create all hashes for their corpus and randomly select 8M random pairs of \emph{simhashes} and flip $h$ random bits on each pair.
The results of these tests can be seen in Figure~\ref{fig:vosh-performance}.

The authors compared their VOSH-algorithm to random hash comparison and were able to show that there exists significant speedup up to 61 times for 100\% recall and a hamming distance of 3 in Figure~\ref{fig:vosh-performance} (d).

\begin{figure}[H]
    \includegraphics[scale=0.35]{./gfx/vosh-performance.png}
    \centering
    \caption{Performance results comparing random comparison search and volatility order based search.}\label{fig:vosh-performance}
\end{figure}
